Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-11-03 papers/thesis-kirstie/thesis.tex
some comments and fixes in section 3.3

@@

We use Soft Fundamental Measure Theory to form a functional for the excess 
Helmholtz free energy appropriate for the WCA fluid by introducing our 
temperature dependent parameters $\alpha(T)$ and $\Xi(T)$. The functional 
is written in general form as 
\begin{align}
  F_{excess}[n(\vec{r})]=k_BT\int(\Phi_1(\vec{r})+\Phi_2(\vec{r})+\Phi_3(\vec{r}{)) d}\vec{r}
\end{align}
where
\begin{align}
\Phi_1 &= -n_{0}\ln(1-n_{3}) \\
\Phi_2 &= \frac{n_{1}n_{2}-\vec{n_{1}}\cdot\vec{n_{2}}}{1-n_{3}} \\
\Phi_3 &= \frac{{n_2}^3-3n_2\vec{n}_{v2}\cdot\vec{n}_{v2}+\frac{9}{2}[\vec{n}_{v2}\cdot{\overleftrightarrow{n}_{m2}}\cdot{\vec{n}_{v2}}-\operatorname{Tr}({\overleftrightarrow{n}^3_{m2}})]}{24\pi(1-n_3)^2}  
\end{align} 
and Tarazona's tensor expression~\cite{tarazonaphi3, santos2012phi3} is used 
for $\Phi_3$. The weigthed densities $n_0, n_1, n_2,$ and $n_3$ are found from
\begin{equation}{n_i(\vec{r})=\int_{Volume}{n(\vec{r'})w_i(|\vec{r}-\vec{r'}|)d{\vec{r'}}}}\end{equation}
where the number density profile $n(\vec r)$ within the integral is given 
by a Gaussian function centered at a lattice point,
%\begin{align}
  %n(\vec r)=(1-f_v)\frac{\exp^{-\frac{r^2}{2{\sigma}^2}}}{\left(\sqrt{2\pi}\sigma\right)^3}
%\end{align}
and the weight functions $w_0, w_1, w_2,$ and $w_3$ are given by
\begin{align}\label{eq:weights}
  w_{0}(r) &=\frac{w_{2}}{4\pi{r}^2} \\
  w_{1}(r) &=\frac{w_{2}}{4\pi{r}} \\
  w_2(r)&=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2}
  \\
  w_3(r)&=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]
\end{align}
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_actual.png}
    %\caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    %view of $w_2$ centered at $\vec{r}'$ is shown in purple. Here, the weight function 
    %is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    %is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure}

Figure \ref{fig:weight_functions} shows a one dimensional view of the weight functions 
$w_0$, $w_1$, $w_2$, $w_3$ as they vary with distance along the z-axis. In three 
dimensions, the weighting functions $w_0$, $w_1$, $w_2$ are spherical shells 
centered at $\vec{r}$. As shown in the cross-sectional view in Figure \ref{fig:W0andW3}a, 
$w_2$ peaks at a radius of $|\vec{r}-\vec{r'}|=\frac{\alpha}{2}$, a width determined 
by $\frac{\Xi}{\sqrt{2}}$, and edges that tapers off on either side of the peak giving 
the shell. The weighting function $w_3$, shown in Figure \ref{fig:W0andW3}b is a solid 
sphere up to $\frac{\alpha-4\Xi}{2}$ after which it tapers off. 
$\Xi$ is related to the width of the functions which 
become wider in general as the temperature increases. 
The radial distance 
to the peak is related to $\alpha$, and decreases as the temperature 
increases, that is, the shells shrink, as does 
the sphere.

@@

The weight fucntions $w_{2}(r)$ and $w_{3}(r)$ are constructed using 
Schmidt's proposed erf model~\cite{schmidt2000fluid} in which he set
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]\end{equation} 
where $w_3(r)$ is subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
%\color{red}These boundary conditions are satisfied for $\Xi{\sqrt{2}<<\alpha}$, or $k_BT << 2.21$. \color{black} 
Our functional is  created by replacing Schmidt's parameters $\sigma$ 
and $a$ with our temperature dependent parameters $\alpha(T)$ and $\Xi(T)$.
\begin{equation}\sigma = \alpha(T)\text{~~~~~~~and~~~~~~~} a = \Xi(T)\end{equation}

The two parameters $\alpha$ and $\Xi$ are used to compensate for the 
temperature dependence that enters in through the expression for the 
error function potential $V_{erf}(r)$ which is used to approximate the
non-temperature dependent WCA potential that is more difficult to 
implement computationally. The erf potential emerges from the relationships
that the weight functions must satisfy.
%potential at temperatures of interest will be used instead of the WCA potential. 
Using Equation~\ref{w2_w3_relation}, shown again below, 
\begin{displaymath}{w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)}\end{displaymath}
and solving for $w_2(r)$
\begin{displaymath}{\frac{dw_3(r)}{dr}\bigg|_{\infty}-\frac{dw_3(r)}{dr}\bigg|_{r}=w_2(r)}\end{displaymath} 
we get \begin{equation}{ w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2} }\end{equation} %From the deconvolution equation \begin{equation}{-\frac{1}{2}f(r)=w_0*w_3 + w_1*w_2 -\vec{w}_{V1}*\vec{w}_{V2}}\end{equation} it follows that $w_2$ must satisfy the relation
Putting $w_2(r)$ into Equation~\ref{mayerder=w2convolution}, shown again below, 
\begin{displaymath}{\frac{df(r)}{dr}=\int_{-\infty}^{\infty}{w_2(r')w_2(r-r')dr'}}\end{displaymath}
gives
\begin{equation}{\frac{df(r)}{dr}=\frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\alpha}{\Xi}\right)^2}}\end{equation} 
which can be integrated to obtain the Mayer function
\begin{equation}{f(r)=\int_{\infty}^r{ \frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r'-\alpha}{\Xi}\right)^2}{dr'}}}\end{equation} 
The Mayer function for the error function potential $V_{erf}(r)$ is thus 
given by
\begin{equation}{f(r)=-\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)\right]}\end{equation} 
Combining this result with the definition of the Mayer function \begin{displaymath}f(r)=e^{-\frac{V(r)}{K_BT}}-1\end{displaymath} 
%This gives an interatomic potential of \begin{equation}{V_{erf}=-k_BT\ln(f(r)-1)}\end{equation} 
gives an expression for the for the error function potential  $V(r)=V_{erf}(r)$ 
\begin{equation}
	V_{erf}(r)=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]
\end{equation}

Expressions for $\alpha(T)$ and $\Xi(T)$  can be found as follows. 
The parameter $\alpha(T)$ is derived by setting 
the erf potential equal to the WCA potential when r equals $\alpha$ 
\begin{equation}{V_{erf}(r=\alpha)=V_{WCA}(r=\alpha)}\end{equation} 
and is given by 
\begin{equation}\label{alphaT}
	{\alpha(T)=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation} 
Figure \ref{fig:alphaXivsT} shows how $\alpha$ varies with temperature 
when $\sigma=1$ and $\epsilon=1$.    
\begin{figure}[h!]
    \centering
    \includegraphics[height=9cm]{plot_alpha.pdf}
    \caption{Shows the temperature dependence of $\alpha$ vs $k_BT/{\epsilon}$ 
    for $\sigma=1$ and $\epsilon=1$}
    \label{fig:alphaXivsT}
  \end{figure}
The value of $\Xi$ at a given temperature, T, can be found computationally 
by equating the second virial coefficient evaluated for the error function 
potential $V_{erf}(r)$, and the second virial coefficent evalued for the 
WCA potential $V_{WCA}$.
\begin{equation}B_{2erf}(T) =B_{2WCA}(T)\end{equation}
The second virial coefficient can be derived from Euler's equation for 
the internal energy of a system, 
\begin{equation}U=TS-PV+\mu{N}\end{equation}
using the relations
\begin{equation}S=-k_B\sum_{i=0}^\infty{P_i\ln{P_i}}\end{equation}
\begin{equation}U=<E>=\sum_{i=0}^\infty{P_iE_i}\end{equation}
\begin{equation}N=<n>=\sum_{i=0}^\infty{P_in_i}\end{equation}
which, for a canonical ensemble, gives
\begin{equation}\frac{PV}{k_BT}=N + \beta\frac{\partial{F}_{excess}}{\partial{N}}{N} - \frac{F_{excess}}{k_BT}\end{equation}
Expressing the Helmholtz free energy in terms of the pair potential 
$V(r)$ results in an equation of state expressed in terms of the virial expansion 
\begin{equation}\label{virialequation}
    \frac{PV}{k_BT}=N\left(1+\frac{N}{V}B_2(T)+\left(\frac{N}{V}\right)^2B_3(T)+ \cdot\cdot\cdot\right) 
\end{equation}
where 
\begin{equation}
	B_{2}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}(r)}-1\right)d\vec{r} 
\end{equation}
Evaluating $B_{2}$ for the erf potential gives
\begin{equation}
	B_{2erf}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{erf}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]
\end{equation}
where $\alpha(T)$ is given by Equation~\ref{alphaT}. Similarly, 
$B_{2WCA}$ can be found computationally from 
\begin{equation}
	B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} 
\end{equation}

A plot of the resulting second virial coefficient $B_2(T)$  with respect 
to temperature is given in Figure~\ref{fig:B2vsT}, and a plot of $\Xi(T)$ obtained 
through this method is shown in Figure~\ref{fig:xi_fromB2vsT}. 
Figure~\ref{fig:erf_Potential_xifromB2} shows the erf potential generated with
$\alpha(T)$ and $\Xi(T)$ at a few different temperatures alongside the WCA 
potential which is not temperature dependent.

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{B2_vs_T_with_xi_fromB2.pdf}
    \caption{Shows the temperature dependence of $B_2$ generated from 
    matching the second virial coeficients for $V_{erf}(r)$ and $V_{WCA}(r)$ 
    at each temperature.}
    \label{fig:B2vsT}
  \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{xi_fromB2.pdf}
    \caption{Shows the temperature dependence of $\Xi$ generated from 
    matching the second virial coeficients for $V_{erf}(r)$ and $V_{WCA}(r)$ 
    at each temperature.}
    \label{fig:xi_fromB2vsT}
  \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{erf_Potential_xifromB2.pdf}
    \caption{Error Function Potential $V_{erf}(r)$ at several temperatures 
    with $\sigma=1$, $\epsilon=1$, compared to the WCA potential $V_{WCA}(r)$ 
    shown in black.}
    \label{fig:erf_Potential_xifromB2}
  \end{figure}

@@

\section{Second Virial Coefficient $B_{2}$ for the Error Function Potential $V_{erf}$}
\begin{equation}B_2=-\frac{1}{2}\int_{allspace}f(\vec{r})d\vec r\end{equation}
The mayer function for the Error Function potential $V_{erf}$ is
\begin{equation}f(r)=\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]\end{equation} from which it can be seen that $f(r)$ is approximately 0 for $r>r_{max}$ where $r_{max}$ is some maximum value of $r$.
\begin{align}
 B_2 &= -\frac{1}{2}\int_0^{\pi}\int_0^{2\pi}\int_0^\infty\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2\sin{\theta}d{\theta}d{\phi}dr \\
     &= -\frac{1}{2}4\pi\frac{1}{2}\int_{0}^{r_{max}}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2dr \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \pi\int_0^{r_{max}}r^2dr   \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \frac{\pi}{3}r_{max}^3   
\end{align}

@@

The Mayer function for the Error Function potential $V_{erf}$, and its Fourier Transform are
\begin{equation}f_{erf}(r)=\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]\end{equation}

\begin{equation}\widetilde{f}_{erf}(k)=-\frac{4\pi}{k^3}e^{-\frac{k^2\Xi^2}{4}}\left[\left(1+\frac{k^2\Xi^2}{2}\right)\sin(k\alpha)-k\alpha\cos(k\alpha)\right]\end{equation}

>>>>

\newcommand\davidsays[1]{\textcolor{red}{[\it D: #1]}}

@@

We use Soft Fundamental Measure Theory to form a functional for the excess 
Helmholtz free energy appropriate for the WCA fluid by introducing our 
temperature dependent parameters $\alpha(T)$ and $\Xi(T)$. The functional 
is written in general form as 
\begin{align}
  F_{excess}[n(\vec{r})]=k_BT\int(\Phi_1(\vec{r})+\Phi_2(\vec{r})+\Phi_3(\vec{r}{)) d}\vec{r}
\end{align}
where
\begin{align}
\Phi_1 &= -n_{0}\ln(1-n_{3}) \\
\Phi_2 &= \frac{n_{1}n_{2}-\vec{n_{1}}\cdot\vec{n_{2}}}{1-n_{3}} \\
\Phi_3 &= \frac{{n_2}^3-3n_2\vec{n}_{v2}\cdot\vec{n}_{v2}+\frac{9}{2}[\vec{n}_{v2}\cdot{\overleftrightarrow{n}_{m2}}\cdot{\vec{n}_{v2}}-\operatorname{Tr}({\overleftrightarrow{n}^3_{m2}})]}{24\pi(1-n_3)^2}  
\end{align} 
and Tarazona's tensor expression~\cite{tarazonaphi3, santos2012phi3} is used 
for $\Phi_3$. The weighted densities $n_0, n_1, n_2,$ and $n_3$ are found from
\begin{equation}{n_i(\vec{r})=\int_{Volume}{n(\vec{r'})w_i(|\vec{r}-\vec{r'}|)d{\vec{r'}}}}\end{equation}
where the number density profile $n(\vec r)$ within the integral is given 
by a Gaussian function centered at a lattice point,
%\begin{align}
  %n(\vec r)=(1-f_v)\frac{\exp^{-\frac{r^2}{2{\sigma}^2}}}{\left(\sqrt{2\pi}\sigma\right)^3}
%\end{align}
and the weight functions $w_0, w_1, w_2,$ and $w_3$ are given by
\begin{align}\label{eq:weights}
  w_{0}(r) &=\frac{w_{2}}{4\pi{r}^2} \\
  w_{1}(r) &=\frac{w_{2}}{4\pi{r}} \\
  w_2(r)&=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2}
  \\
  w_3(r)&=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]
\end{align}
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_actual.png}
    %\caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    %view of $w_2$ centered at $\vec{r}'$ is shown in purple. Here, the weight function 
    %is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    %is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure}

Figure \ref{fig:weight_functions} shows a one dimensional view of the weight functions 
$w_0$, $w_1$, $w_2$, $w_3$ as they vary with distance along the z-axis. In three 
dimensions, the weighting functions $w_0$, $w_1$, $w_2$ are spherical shells 
centered at $\vec{r}$. As shown in the cross-sectional view in Figure \ref{fig:W0andW3}a, 
$w_2$ peaks at a radius of $|\vec{r}-\vec{r'}|=\frac{\alpha}{2}$, with a width determined 
by $\frac{\Xi}{\sqrt{2}}$, and edges that tapers off on either side of the peak giving 
the shell. The weighting function $w_3$, shown in Figure \ref{fig:W0andW3}b is a solid 
sphere up to $\frac{\alpha-4\Xi}{2}$ after which it tapers off. 
$\Xi$ is related to the width of the functions which 
become wider in general as the temperature increases. 
The radial distance 
to the peak is related to $\alpha$, and decreases as the temperature 
increases, that is, the shells shrink, as does 
the sphere.

@@

\davidsays{Maybe say this before presenting the weights? But also, I don't think
there is any benefit to introducing $a$ and $\sigma$ here.} The weight functions $w_{2}(r)$ and $w_{3}(r)$ are constructed
using 
Schmidt's proposed erf model~\cite{schmidt2000fluid} in which he set
\begin{equation}
  w_3(r)=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]
\end{equation} 
where $w_3(r)$ is subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
%\color{red}These boundary conditions are satisfied for $\Xi{\sqrt{2}<<\alpha}$, or $k_BT << 2.21$. \color{black} 
Our functional is  created by replacing Schmidt's parameters $\sigma$ 
and $a$ with temperature-dependent parameters $\alpha(T)$ and $\Xi(T)$.
\begin{equation}\sigma = \alpha(T)\text{~~~~~~~and~~~~~~~} a = \Xi(T)\end{equation}

The two parameters $\alpha$ and $\Xi$ are used to compensate for the 
temperature dependence that enters in through the expression for the 
error function potential $V_{\operatorname{erf}}(r)$ which is used to approximate the
non-temperature dependent WCA potential that is more difficult to 
implement computationally. The erf potential emerges from the relationships
that the weight functions must satisfy\davidsays{In order for what?}.
%potential at temperatures of interest will be used instead of the WCA potential. 
Using Equation~\ref{w2_w3_relation}, shown again below, 
\begin{align}
  w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)
\end{align}
and solving for $w_2(r)$
\begin{align}
  \frac{dw_3(r)}{dr}\bigg|_{\infty}-\frac{dw_3(r)}{dr}\bigg|_{r}=w_2(r)
\end{align} 
we get \begin{equation}{ w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2} }\end{equation} %From the deconvolution equation \begin{equation}{-\frac{1}{2}f(r)=w_0*w_3 + w_1*w_2 -\vec{w}_{V1}*\vec{w}_{V2}}\end{equation} it follows that $w_2$ must satisfy the relation
Putting $w_2(r)$ into Equation~\ref{mayerder=w2convolution}, shown again below, 
\begin{displaymath}{\frac{df(r)}{dr}=\int_{-\infty}^{\infty}{w_2(r')w_2(r-r')dr'}}\end{displaymath}
gives
\begin{equation}{\frac{df(r)}{dr}=\frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\alpha}{\Xi}\right)^2}}\end{equation} 
which can be integrated to obtain the Mayer function
\begin{equation}{f(r)=\int_{\infty}^r{ \frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r'-\alpha}{\Xi}\right)^2}{dr'}}}\end{equation} 
The Mayer function for the error function potential $V_{\operatorname{erf}}(r)$ is thus 
given by
\begin{equation}{f(r)=-\frac{1}{2}\left[1-\operatorname{\operatorname{erf}}\left(\frac{r-\alpha}{\Xi}\right)\right]}\end{equation} 
Combining this result with the definition of the Mayer function \begin{displaymath}f(r)=e^{-\frac{V(r)}{K_BT}}-1\end{displaymath} 
%This gives an interatomic potential of \begin{equation}{V_{\operatorname{erf}}=-k_BT\ln(f(r)-1)}\end{equation} 
gives an expression for the for the error function potential  $V(r)=V_{\operatorname{erf}}(r)$ 
\begin{equation}
	V_{\operatorname{erf}}(r)=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]
\end{equation}

Expressions for $\alpha(T)$ and $\Xi(T)$  can be found as follows. 
The parameter $\alpha(T)$ is derived by setting 
the erf potential equal to the WCA potential when $r=\alpha$, i.e. at the
maximum of $w_2(r)$,
% \begin{equation}{V_{\operatorname{erf}}(r=\alpha)=V_{WCA}(r=\alpha)}\end{equation} 
which gives us
\begin{equation}\label{alphaT}
	{\alpha(T)=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation} 
Figure \ref{fig:alphaXivsT} shows how $\alpha$ varies with temperature 
when $\sigma=1$ and $\epsilon=1$.    
\begin{figure}[h!]
    \centering
    \includegraphics[height=9cm]{plot_alpha.pdf}
    \caption{Shows the temperature dependence of $\alpha$ vs $k_BT/{\epsilon}$ 
    for $\sigma=1$ and $\epsilon=1$}
    \label{fig:alphaXivsT}
  \end{figure}
We determine value of $\Xi$ at a given temperature $T$,
by equating the second virial coefficient evaluated for the error function 
potential $V_{\operatorname{erf}}(r)$, and the second virial coefficent evalued for the 
WCA potential $V_{WCA}$.
\begin{equation}B_{2\operatorname{erf}}(T) =B_{2WCA}(T)\end{equation}
\davidsays{I think we'd benefit from cutting much of the following, since you
show the standard equations, but skip the bit where we put in the pair potential,
which is the tricky step.}
The second virial coefficient can be derived from Euler's equation for 
the internal energy of a system, 
\begin{equation}U=TS-PV+\mu{N}\end{equation}
using the relations
\begin{equation}S=-k_B\sum_{i=0}^\infty{P_i\ln{P_i}}\end{equation}
\begin{equation}U=\langle E\rangle=\sum_{i=0}^\infty{P_iE_i}\end{equation}
\begin{equation}N=\langle n\rangle=\sum_{i=0}^\infty{P_in_i}\end{equation}
which, for a canonical ensemble, gives
\begin{equation}\frac{PV}{k_BT}=N + \beta\frac{\partial{F}_{excess}}{\partial{N}}{N} - \frac{F_{excess}}{k_BT}\end{equation}
Expressing the Helmholtz free energy in terms of the pair potential 
$V(r)$ results in an equation of state expressed in terms of the virial expansion 
\begin{equation}\label{virialequation}
    \frac{PV}{k_BT}=N\left(1+\frac{N}{V}B_2(T)+\left(\frac{N}{V}\right)^2B_3(T)+ \cdot\cdot\cdot\right) 
\end{equation}
where 
\begin{equation}
	B_{2}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}(r)}-1\right)d\vec{r} 
\end{equation}
Evaluating $B_{2}$ for the erf potential gives
\begin{equation}
	B_{2\operatorname{erf}}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{\operatorname{erf}}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]
\end{equation}
where $\alpha(T)$ is given by Equation~\ref{alphaT}. Similarly, 
$B_{2WCA}$ can be found computationally from 
\begin{equation}
	B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} 
\end{equation}

\davidsays{Some of this is worth showing, but I think you're giving too many
plots here.
In general, we'd like to only show plots if we have something to say about them,
so either we want more words, or fewer figures.  e.g. what does the reader learn
from looking at your plot of $B_2$ versus $T$? If there is something they should
learn from it, then you should write that down, so they don't have to figure it
out on their own.  If there isn't anything to say, then probably you can skip
it. There \emph{are} times to just show a plot, but it's usually if it's an
prediction, and you want to say \emph{something} about the plot beyond its
existence.}
A plot of the resulting second virial coefficient $B_2(T)$  with respect 
to temperature is given in Figure~\ref{fig:B2vsT}, and a plot of $\Xi(T)$ obtained 
through this method is shown in Figure~\ref{fig:xi_fromB2vsT}. 
Figure~\ref{fig:erf_Potential_xifromB2} shows the erf potential generated with
$\alpha(T)$ and $\Xi(T)$ at a few different temperatures alongside the WCA 
potential which is not temperature dependent.

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{B2_vs_T_with_xi_fromB2.pdf}
    \caption{Shows the temperature dependence of $B_2$ generated from 
    matching the second virial coeficients for $V_{\operatorname{erf}}(r)$ and $V_{WCA}(r)$ 
    at each temperature.}
    \label{fig:B2vsT}
  \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{xi_fromB2.pdf}
    \caption{Shows the temperature dependence of $\Xi$ generated from 
    matching the second virial coeficients for $V_{\operatorname{erf}}(r)$ and $V_{WCA}(r)$ 
    at each temperature.}
    \label{fig:xi_fromB2vsT}
  \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{erf_Potential_xifromB2.pdf}
    \caption{Error Function Potential $V_{\operatorname{erf}}(r)$ at several temperatures 
    with $\sigma=1$, $\epsilon=1$, compared to the WCA potential $V_{WCA}(r)$ 
    shown in black.}
    \label{fig:erf_Potential_xifromB2}
  \end{figure}

@@

\section{Second Virial Coefficient $B_{2}$ for the Error Function Potential $V_{\operatorname{erf}}$}
\begin{equation}B_2=-\frac{1}{2}\int_{allspace}f(\vec{r})d\vec r\end{equation}
The mayer function for the Error Function potential $V_{\operatorname{erf}}$ is
\begin{equation}f(r)=\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]\end{equation} from which it can be seen that $f(r)$ is approximately 0 for $r>r_{max}$ where $r_{max}$ is some maximum value of $r$.
\begin{align}
 B_2 &= -\frac{1}{2}\int_0^{\pi}\int_0^{2\pi}\int_0^\infty\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2\sin{\theta}d{\theta}d{\phi}dr \\
     &= -\frac{1}{2}4\pi\frac{1}{2}\int_{0}^{r_{max}}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2dr \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \pi\int_0^{r_{max}}r^2dr   \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \frac{\pi}{3}r_{max}^3   
\end{align}

@@

The Mayer function for the Error Function potential $V_{\operatorname{erf}}$, and its Fourier Transform are
\begin{equation}f_{\operatorname{erf}}(r)=\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]\end{equation}

\begin{equation}\widetilde{f}_{\operatorname{erf}}(k)=-\frac{4\pi}{k^3}e^{-\frac{k^2\Xi^2}{4}}\left[\left(1+\frac{k^2\Xi^2}{2}\right)\sin(k\alpha)-k\alpha\cos(k\alpha)\right]\end{equation}
